### 2022-01-17 src-latex/parts/40-ner-approaches.tex
ner models eval : tables & figures

\subsubsection{Regexp}
::TODO::
Needed for experiment 2 ?

@@

\subsubsection{CamemBERT \& CamemBERT+pretrained on raw entries}
::TODO::

@@

For our experiments, two models are derived. One is produced by fine-tuning this generic model on our ground truth dataset.
The second is created by adapting the embeddings of this model using raw directory texts, randomly selected and extracted with PERO OCR. The base model is pretrained on these texts for two tasks, namely, Next Sentence Prediction (NSP) and Masked Language Model (MLM). Finally, the resulting model is also fine-tuned using our ground truth corpus.

>>>>

@@

\subsubsection{CamemBERT \& CamemBERT pretrained on raw entries}

@@

For our experiments, two models are derived. One is produced by fine-tuning this generic model on our ground truth dataset.
The second is created by adapting the embeddings of this model using 845 000 raw directory entries, randomly selected and extracted with PERO OCR. The base model is pretrained on these texts for two tasks, namely, Next Sentence Prediction (NSP) and Masked Language Model (MLM). Finally, the resulting model is also fine-tuned using our ground truth corpus.
